---
title: "R Basics"
output: html_notebook
---
#3.3 Excercise

1. What is the sum of the first 100 positive integers? 
```{r}
n <- 100
n*(n + 1) / 2

```

2. Now use the same formula to compute the sum of the integers from 1 through 1,000.
```{r}
n <- 1000
n*(n + 1) / 2

```

3. Look at the result of typing the following code into R:
```{r}
n <- 1000
x <- seq(1, n)
sum(x)
```

4. Use one line of code to compute the log, in base 10, of the square root of 100.
```{r}
log(100, base=10)
```

5. Which of the following will always return the numeric value stored in x? 
```{r}
log(exp(x))

```


#.3.6 Exercise

1. Load the US murders dataset.
```{r}
library(dslabs)
data(murders)

```

2. What are the column names used by the data frame for these five variables?
```{r}
names(murders)
```

3. Use the accessor $ to extract the state abbreviations and assign them to the object a. What is the class of this object?
```{r}
a <- (murders$abb)
class(a)
```

4. Now use the square brackets to extract the state abbreviations and assign them to the object b. Use the identical function to determine if a and b are the same.
```{r}
b <- murders[ ,2] 
identical(a, b)
```

5. We saw that the region column stores a factor. You can corroborate this by typing.
With one line of code, use the function levels and length to determine the number of regions defined by this dataset. 
```{r}
class(murders$region)
levels(murders$region)
length(murders$region)

```

6. The function table takes a vector and returns the frequency of each element. You can quickly see how many states are in each region by applying this function. Use this function in one line of code to create a table of states per region.
```{r}
table(murders$state,murders$region)

```

#.3.9 Exercises

1. Use the function c to create a vector with the average high temperatures in January for Beijing, Lagos, Paris, Rio de Janeiro, San Juan and Toronto, which are 35, 88, 42, 84, 81, and 30 degrees Fahrenheit. Call the object temp.
2. Now create a vector with the city names and call the object city.
```{r}
temp <- c(35, 88, 42, 84, 81, 30)
city <- c('Beijing', 'Lagos', 'Paris', 'Rio de Janeiro', 'San Juan', 'Toronto')
temp 
```

3. Use the names function and the objects defined in the previous exercises to associate the temperature data with its corresponding city.
```{r}
names(temp) <- city
temp 

```

4. Use the [ and : operators to access the temperature of the first three cities on the list.
```{r}
temp[c(1:3)]


```

5. Use the [ operator to access the temperature of Paris and San Juan.
```{r}
temp[c(3,5)]

```

6. Use the : operator to create a sequence of numbers 12, 13, 14, …, 73.
```{r}
12:73

```

7. Create a vector containing all the positive odd numbers smaller than 100.
```{r}
seq(1, 100, 2)
```

8. Create a vector of numbers that starts at 6, does not pass 55, and adds numbers in increments of 4/7: 6, 6+4/7, 6+8/7, etc.. How many numbers does the list have? Hint: use seq and length.
```{r}
length(seq(6, 55, 4/7))

```

9. What is the class of the following object a <- seq(1, 10, 0.5)?
```{r}
a <- seq(1, 10, 0.5)
class(a)

```

10. What is the class of the following object a <- seq(1, 10)?
```{r}
a <- seq(1, 10)
class(a)

```

11. The class of class(a<-1) is numeric, not integer. R defaults to numeric and to force an integer, you need to add the letter L. Confirm that the class of 1L is integer.
```{r}
a <- 1
b <- 1L
class(b)

```

12. Define the following vector, and coerce it to get integers
```{r}
x <- c("1", "3", "5")
as.integer(x)

```


#3.11 Exercise

1. Use the $ operator to access the population size data and store it as the object pop. Then use the sort function to redefine pop so that it is sorted. Finally, use the [ operator to report the smallest population size.
```{r}
sort(murders$population)
min(murders$population) 

```

2. Now instead of the smallest population size, find the index of the entry with the smallest population size. Hint: use order instead of sort.
```{r}
order(murders$population)

```

3. We can actually perform the same operation as in the previous exercise using the function which.min. Write one line of code that does this.
```{r}
which.min(murders$population)

                  
```

4. Now we know how small the smallest state is and we know which row represents it. Which state is it? Define a variable states to be the state names from the murders data frame. Report the name of the state with the smallest population.
```{r}
i_min <- which.min(murders$population)
murders$state[i_min]

```

5. Use the rank function to determine the population rank of each state from smallest population size to biggest. Save these ranks in an object called ranks, then create a data frame with the state name and its rank. Call the data frame my_df.
```{r}
ranks <- rank(murders$population)
name <- c(murders$state)
my_df <- data.frame(name = name, rank = ranks)
my_df

```

6. Repeat the previous exercise, but this time order my_df so that the states are ordered from least populous to most populous. Hint: create an object ind that stores the indexes needed to order the population values. Then use the bracket operator [ to re-order each column in the data frame.
```{r}
ind <- order(murders$population)
murders$state[ind]

```


#.3.13 Exercises

1. Previously we created this data frame.
Remake the data frame using the code above, but add a line that converts the temperature from Fahrenheit to Celsius. 
```{r}
city_temps <- data.frame(name = city, temperature = temp)

celcius <- 5/9 * (temp - 32)
celcius
```

2. What is the following sum 1 + 1/2^2 + 1/3^2 + ... + 1/100^2?
```{r}
n <- (1:100)
sum(1/n^2)

```

3. Compute the per 100,000 murder rate for each state and store it in the object murder_rate. Then compute the average murder rate for the US using the function mean. What is the average?
```{r}
x <- c(murders$total)
y <- c(murders$population)
murder_rate <- c((x / y) * 100000)
mean(murder_rate)

```


#.3.15 Exercises

1. Compute the per 100,000 murder rate for each state and store it in an object called murder_rate. Then use logical operators to create a logical vector named low that tells us which entries of murder_rate are lower than 1.
```{r}
low <- murder_rate < 1
murders$state[low]
```

2. Now use the results from the previous exercise and the function which to determine the indices of murder_rate associated with values lower than 1.









