---
title: "The tidyverse"
output: html_notebook
---

#. Intro
```{r}
library(tidyverse)
```

#. 5.2 Exercise
```{r}
data(co2)
head(co2)
```
A. co2 is tidy data: it has one year for each row.

B. co2 is not tidy: we need at least one column with a character vector.

C. co2 is not tidy: it is a matrix instead of a data frame.

D. co2 is not tidy: to be tidy we would have to wrangle it to have three columns (year, month and value), then each co2 observation would have a row.

-> Answer> C.

```{r}
data("ChickWeight")
head(ChickWeight)
```
A. ChickWeight is not tidy: each chick has more than one row.

B. ChickWeight is tidy: each observation (a weight) is represented by one row. The chick from which this measurement came from is one the variables.

C. ChickWeight is not a tidy: we are missing the year column.

D. ChickWeight is tidy: it is stored in a data frame.

-> Anser> B.

```{r}
data(BOD)
head(BOD)
```
A. BOD is not tidy: it only has six rows.

B. BOD is not tidy: the first column is just an index.

C. BOD is tidy: each row is an observation with two values (time and demand)

D. BOD is tidy: all small datasets are tidy by definition.

-> Anser> C.

